Description of a Deterministic Unit Commitment Model with Probabilistic Reserve constraints and Network Representation

### 2022-04-27 papers/main.tex
Investigating feasability issues
Update model description

All variables are positive.

\begin{itemize}
    \item $q_{gt}$ - Generation
    \item $\hat{q}_{gt}$ - Generation above the minimum stable operating point (0 in the case of renewables).
    \item $ls_{nt}$ - Load shedding
    \item $inj_{nt}$ - Node injection
    \item $f_{lt}$ - Branch flow
    \item $r^+_{gt}$ - Total upward reserve provision
    \item $r^-_{gt}$ - Total downward reserve provision
    \item $r^{L^+}_{glt}$ - Upward reserve provision for reserve level $l$
    \item $r^{L^-}_{glt}$ - Downward reserve provision for reserve level $l$
    \item $rs_{glt}$ - Upward reserve shedding for reserve level $l$
\end{itemize}

@@

\begin{align}
    \min \quad & \sum_{t \in T} \sum_{g \in G} C^{var}_{g} \cdot \hat{q}_{gt} \nonumber                                          \\
               & \sum_{t \in T} \sum_{l \in L^+} P^{L^+} \cdot \sum_{g \in G} C^{var}_{g} \cdot r^{L^+}_{glt} + C^{shed} \cdot rs_{lt} \\
               & \sum_{t \in T} \sum_{l \in L^-} P^{L^-} \cdot C^{var}_{g} \cdot r^{L^-}_{glt} \nonumber
\end{align}

@@

Note the use of the set $G_n$ to only allow generators at node $n$ to contribute to the power balance.

@@

For brevity and clarity, constraints on ramping and minimum up and down times are omitted. In some sense, the commitment variable $z_{gt}$ can be thought of as given.

@@

\begin{align}
    r^{+}_{gt} = \sum_{l \in L^+} r^{L^+}_{glt}           & \quad g \in G, \; t \in T   \\
    r^{-}_{gt} = \sum_{l \in L^-} r^{L^-}_{glt}           & \quad g \in G, \; t \in T   \\
    D^{L^+}_{gt} = \sum_{g \in G} r^{L^+}_{glt} + rs_{lt} & \quad l \in L^+, \; t \in T \\
    D^{L^-}_{gt} = \sum_{g \in G} r^{L^-}_{glt}           & \quad l \in L^-, \; t \in T \\
\end{align}

@@

\begin{itemize}
    \item The operating reserve balance is performed over the entire network, not per node.
    \item The operating reserve balance is split into reserve levels. Higher reserve levels (values of $l$) are less likely to occur.
    \item It is possible to shed upward reserves, and this is more likely to occur for higher reserve levels.
\end{itemize}

@@

\begin{align}
    \sum_{g \in G_n} r^{L^+}_{glt} = rinj^{L^+}_{nlt}                & \quad n \in N, l \in L^+, \; t \in T    \\
    \sum_{g \in G_n} r^{L^-}_{glt} = rinj^{L^-}_{nlt}                & \quad n \in N, l \in L^-, \; t \in T    \\
    rf^{L^+}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^+}_{nlt} & \quad b \in B, l \in L^+, \; t \in T    \\
    rf^{L^-}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^-}_{nlt} & \quad b \in B, l \in L^-, \; t \in T    \\
    -F_{b} \leq rf^{L^+}_{blt} \leq F_b                              & \quad b \in B, \; l \in L^+, \; t \in T \\
    -F_{b} \leq rf^{L^-}_{blt} \leq F_b                              & \quad b \in B, \; l \in L^-, \; t \in T \\
    \sum_{n \in N} rinj^{L^+}_{nt} = 0                               & \quad l \in L^+, \; n \in N, \; t \in T \\
    \sum_{n \in N} rinj^{L^-}_{nt} = 0                               & \quad l \in L^-, \; n \in N, \; t \in T \\
\end{align}

>>>>

All variables are positive apart from injetion variables which may also be negative.

\begin{itemize}
    \item $q_{gt}$ - Generation
    \item $\hat{q}_{gt}$ - Generation above the minimum stable operating point (0 in the case of renewables).
    \item $ls_{nt}$ - Load shedding
    \item $inj_{nt}$ - Node injection
    \item $f_{lt}$ - Branch flow
    \item $r^+_{gt}$ - Total upward reserve provision
    \item $r^-_{gt}$ - Total downward reserve provision
    \item $r^{L^+}_{glt}$ - Upward reserve provision for reserve level $l$
    \item $r^{L^-}_{glt}$ - Downward reserve provision for reserve level $l$
    \item $rs_{nlt}$ - Upward reserve shedding for reserve level $l$
    \item $rc_{nlt}$ - Downward reserve provided by day ahead load shedding for reserve level $l$
    \item $rinj_{nlt}^{L^+}$ - Possible node injection due to activation of upward reserve level $l$
    \item $rinj_{nlt}^{L^-}$ - Possible node injection due to activation of downward reserve level $l$
    \item $rf_{nbt}^{L^+}$ - Possible branch flow due to activation of upward reserve level $l$
    \item $rf_{nbt}^{L^-}$ - Possible branch flow due to activation of downward reserve level $l$
\end{itemize}

@@

\begin{align}
    \min \quad & \sum_{t \in T} \sum_{g \in G} C^{var}_{g} \cdot \hat{q}_{gt} \nonumber                                                                  \\
               & + \sum_{t \in T} \sum_{l \in L^+} \sum_{n \in N} P^{L^+} \cdot \sum_{g \in G} C^{var}_{g} \cdot r^{L^+}_{glt} + C^{shed} \cdot rs_{nlt} \\
               & - \sum_{t \in T} \sum_{l \in L^-} \sum_{n \in N} P^{L^-} \cdot C^{var}_{g} \cdot r^{L^-}_{gnlt} + C^{shed} \cdot rc_{nlt} \nonumber
\end{align}

@@

Note the use of the set $G_n$ to only allow generators at node $n$ to contribute to the power balance. Another way of describing this would have been through an incidence matrix.

@@

For brevity and clarity, constraints on ramping and minimum up and down times are omitted.

@@

\begin{align}
    D^{L^+}_{lt} = \sum_{g \in G} r^{L^+}_{glt} + \sum_{n \in N} rs_{nlt} & \quad l \in L^+, \; t \in T \\
    D^{L^-}_{lt} = \sum_{g \in G} r^{L^-}_{glt} + \sum_{n \in N} rc_{nlt} & \quad l \in L^-, \; t \in T \\
    \sum_{l \in L^-} rc_{nlt} \leq ls_{nt}                                 & \quad n \in N, \; t \in T \\
    r^{+}_{gt} = \sum_{l \in L^+} r^{L^+}_{gnlt}                           & \quad g \in G, \; t \in T   \\
    r^{-}_{gt} = \sum_{l \in L^-} r^{L^-}_{gnlt}                           & \quad g \in G, \; t \in T 
\end{align}

@@

\begin{itemize}
    \item The operating reserve balance is performed over the entire network, not per node.
    \item The operating reserve balance is split into reserve levels. Higher reserve levels (values of $l$) are less likely to occur.
    \item It is possible to shed upward reserves, and this is more likely to occur for higher reserve levels. This model is therefore able to make a tradeoff between day ahead adequacy and real time operational security, albeit crudely.
    \item Shedding load in day ahead allows additional downward reserves to be provided through the variable $rc_{nlt}$. Implicitly this assumes that load can be `activated' in real time to provide downward reserves.
\end{itemize}

@@

\begin{align}
    \sum_{g \in G_n} r^{L^+}_{glt} + rs_{nlt} = rinj^{L^+}_{nlt}                & \quad n \in N, l \in L^+, \; t \in T    \\
    \sum_{g \in G_n} r^{L^-}_{glt} + rc_{nlt} = rinj^{L^-}_{nlt}                & \quad n \in N, l \in L^-, \; t \in T    \\
    rf^{L^+}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^+}_{nlt} & \quad b \in B, l \in L^+, \; t \in T    \\
    rf^{L^-}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^-}_{nlt} & \quad b \in B, l \in L^-, \; t \in T    \\
    -F_{b} \leq rf^{L^+}_{blt} \leq F_b                              & \quad b \in B, \; l \in L^+, \; t \in T \\
    -F_{b} \leq rf^{L^-}_{blt} \leq F_b                              & \quad b \in B, \; l \in L^-, \; t \in T \\
    \sum_{n \in N} rinj^{L^+}_{nt} = 0                               & \quad l \in L^+, \; n \in N, \; t \in T \\
    \sum_{n \in N} rinj^{L^-}_{nt} = 0                               & \quad l \in L^-, \; n \in N, \; t \in T
\end{align}
